Draft genomes of the three northern hemisphere blue mussel lineages: North and South European \emph{Mytilus edulis} and Mediterranean \emph{Mytilus galloprovincialis}.

### 2022-07-08 manuscript/ms_genomes.tex
include mantis db and change version

We used the \texttt{Mantis} pipeline (\url{https://github.com/PedroMTQ/mantis}; commit c6cb597; \cite{Queiros2021}) to obtain consensus functional annotations of genes based on multiple databases.
Protein sequences for each assembly were built from the \texttt{Braker2} annotation using the \texttt{python} module \texttt{gff3tool} (v2).

@@

%\begin{itemize}
%	\item Supernova v2.1.1 \href{https://doi.org/10.1101/gr.214874.116}{cite}
%	\item Longranger v2.2.2
%	\item proc10xG \url{https://github.com/ucdavis-bioinformatics/proc10xG} commit 7afbfcf
%	\item nubeam-dedup \url{https://github.com/daihang16/nubeamdedup} commit 25dd385 \href{https://doi.org/10.1093/bioinformatics/btaa112}{cite}
%	\item KMC \url{https://github.com/tbenavi1/KMC} commit 1df71f6
%	\item GenomeScope 2.0 \url{https://github.com/tbenavi1/genomescope2.0} commit 5034ed4 \href{https://doi.org/10.1038/s41467-020-14998-3}{cite}
%	\item (? Smudgeplot commit 950d7b5)
%	\item Purge\_Dups \url{https://github.com/dfguan/purge_dups} commit e1934bb \href{https://doi.org/10.1093/bioinformatics/btaa025}{cite}
%	\item AGOUTI \url{https://github.com/svm-zhang/AGOUTI} commit a7e65d6 \href{https://doi.org/10.1186/s13742-016-0136-3}{cite}
%	\item augustus v3.3.3 (for AGOUTI analysis) (\protect\hyperlink{ref-Stanke2008}{\textbf{Stanke2008?}})
%	\item Blobtoolkit v2.4.0 \href{https://doi.org/10.1534/g3.119.400908}{cite}
%	\item KAT v2.4.2 \href{https://doi.org/10.1093/bioinformatics/btw663}{cite}
%	\item fastp v0.20.1 (\protect\hyperlink{ref-Chen2018a}{\textbf{Chen2018a?}})
%	\item samtools v1.12 (\protect\hyperlink{ref-Li2009}{\textbf{Li2009?}})
%	\item minimap2 v2.17 (\protect\hyperlink{ref-LiLi2017}{\textbf{LiLi2017?}})
%	\item bwa-mem2 v2.2.1 (\protect\hyperlink{ref-VasimuddinMd2019}{\textbf{VasimuddinMd2019?}})
%	\item bedtools v2.29.2 (\protect\hyperlink{ref-Quinlan2010}{\textbf{Quinlan2010?}})
%	\item seqkit v0.13.2 (\protect\hyperlink{ref-Shen2016}{\textbf{Shen2016?}})
%	\item rcorrector v1.0.4
%	\item trim-galore v0.6.6 \href{https://github.com/FelixKrueger/TrimGalore}{cite} (Cutadapt + FastQC wrapper)
%	\item busco v5.1.1 (\protect\hyperlink{ref-Seppey2019}{\textbf{Seppey2019?}})
%	\item assembly\_stats v0.1.4 \href{https://doi.org/10.5281/zenodo.3968774}{cite}
%	\item ragtag v1.1.1 (\protect\hyperlink{ref-Alonge2019}{\textbf{Alonge2019?}})
%	\item pilon v1.24 (\protect\hyperlink{ref-Walker2014}{\textbf{Walker2014?}})
%	\item TETools DFAM container v1.3.1
%	\item RepeatModeler v2.0.1 (\protect\hyperlink{ref-Flynn2020}{\textbf{Flynn2020?}})
%	\item cd-hit v4.8.1 (\protect\hyperlink{ref-Fu2012}{\textbf{Fu2012?}})
%	\item RepeatMasker v4.1.2-p1 (Smit, AFA, Hubley, R. RepeatModeler Open-1.0. 2008-2015 \url{http://www.repeatmasker.org}) (\protect\hyperlink{ref-Smit2013}{\textbf{Smit2013?}})
%\end{itemize}

@@

\subsection{Annotations}

[[Here goes annotation stats]]

>>>>

We used the \texttt{Mantis} pipeline (v1.5.5; \cite{Queiros2021}) to obtain consensus functional annotations of genes based on multiple databases.
Protein sequences for each assembly were built from the structural annotations using the \texttt{python} module \texttt{gff3tool} (v2).
\texttt{Mantis} was run with default parameters and databases:
kofam \parencite{Aramaki2020}, NPFM \parencite{Lu2020}, eggNOG \parencite{Huerta-Cepas2019}, pfam \parencite{El-Gebali2019}, and tcdb \parencite{Saier2021}.

@@

@@

%\subsection{Annotations}
%
%[[Here goes annotation stats]]
